Updated Constraints on Self-Interacting Dark Matter from Supernova 1987A

### 2017-05-03 draft.tex
updated

Having obtained an expression for $ \kappa $, we can now find the optical depth as follows. 
Define a typical optical depth as $\tau_\mathrm{R} = \kappa_\mathrm{R} \rho_\mathrm{R} R $. We then have 
\beq 
\kappa \rho R = \tau_\mathrm{R} \left( \frac{\rho}{\rho_\mathrm{R}} \right)^2 \left( \frac{T_\mathrm{R}}{T} \right)^{3/2}.
\eeq
%
This can be combined with the previous expressions for the density and temperature as a function of position 
and plugged in to the integral expression for the optical depth to obtain 
\bea 
\tau &=& \int_{r_x}^{\infty}\, \tau_\mathrm{R} \left( \frac{R}{r} \right)^{3n/2} \dd r \\
 &=& \frac{\tau_\mathrm{r}}{\frac{3n}{2}-1} \left( \frac{T_\mathrm{A'}}{T_\mathrm{R}} \right)^{(9/2-3/n)}. 
 \eea
 The bound on the coupling is obtained by requiring  $ \tau(\varepsilon,m_\mathrm{A'}) \le 2/3 $

>>>>

Having obtained an expression for $ \kappa $, we can now find the optical depth as follows. 
Define a typical optical depth as $\tau_\mathrm{R} = \kappa_\mathrm{R} \rho_\mathrm{R} R $. We then have 
\beq 
\kappa \rho R = \tau_\mathrm{R} \left( \frac{\rho}{\rho_\mathrm{R}} \right)^2 \left( \frac{T_\mathrm{R}}{T} \right)^{3/2}.
\eeq
%
This can be combined with the previous expressions for the density and temperature as a function of position 
and plugged in to the integral expression for the optical depth to obtain 
\bea 
\tau &=& \int_{r_x}^{\infty}\, \tau_\mathrm{R} \left( \frac{R}{r} \right)^{3n/2} \dd r \\
 &=& \frac{\tau_\mathrm{r}}{\frac{3n}{2}-1} \left( \frac{T_\mathrm{A'}}{T_\mathrm{R}} \right)^{(9/2-3/n)}. 
 \eea
 The bound on the coupling is obtained by requiring  $ \tau(\varepsilon,m_\mathrm{A'}) \le 2/3 $. Note that strictly speaking we should have determined $ r_{\mathrm{dp}} $ rather than assuming a value. To check if our assumption is valid we can go backwards through the calculation and determine the value of $ r_{\mathrm{dp}} $ at which $ \tau = 2/3$. Doing so we find that our choice of 10 km is roughly correct.
